SunPy - Python for Solar Physics

### 2014-08-26 1-Introduction.tex

A typical workflow begins with a solar physicist manually identifying
a small number of events of interest on the Sun.  This is typically
done in order to investigate in detail the physics of these events
(for example, the large solar flare of 23 July 2002 has a volume of
the Astrophysical Journal dedicated to it).  In this workflow, data
from many different instruments are obtained.  These data are
typically in many different storage formats (for example, FITS, CSV,
or binary files), and contain many different types of data (such as
images, lightcurves and spectra).  The repositories these data reside
in can have different access methods.  This workflow is characterized
by the large number of heterogeneous datasets used in the
investigation of a small number of solar events.

>>>>

A typical workflow begins with a solar physicist manually identifying
a small number of events of interest on the Sun.  This is typically
done in order to investigate in detail the physics of these events
(for example, the large solar flare of 23 July 2002 has Astrophysical
Journal Letters volume 595, dedicated to the analysis of this flare).
In this workflow, data from many different instruments are obtained.
These data are typically in many different storage formats (for
example, FITS, CSV, or binary files), and contain many different types
of data (such as images, lightcurves and spectra).  The repositories
these data reside in can have different access methods.  This workflow
is characterized by the large number of heterogeneous datasets used in
the investigation of a small number of solar events.
